Software Citation Principles

### 2016-03-07 sc-principles/software-citation-principles.tex
adding bullet headings

There are many reasons this lack of both software citations in general and standard practices
for software citation are of concern:
\begin{itemize}
\item Software is a product of research, and by not citing it, we leave holes in the record of of scientific progress.
\item Academic researchers at all levels, including students, postdocs, faculty, and staff, should be
credited for the software products they develop and contribute to, particularly when those products enable or further research done by others.
\end{itemize}

>>>>

There are many reasons this lack of both software citations in general and standard practices
for software citation are of concern:
\begin{itemize}
\item Understanding Science: Software is a product of research, and by not citing it, we leave holes in the record of of scientific progress.
\item Academic Credit: Academic researchers at all levels, including students, postdocs, faculty, and staff, should be
credited for the software products they develop and contribute to, particularly when those products enable or further research done by others.
\end{itemize}
